Nonlinear Model 
========
```{r}
require(ISLR)
attach(Wage)
```

Polynomials 
------------
First we will use polynomials, and focus on a single predictor age:

```{r}
fit = lm(wage ~ poly(age, 4), data = Wage)
summary(fit)
```

The `ploy()` function generates a basis of *orthogonal polynomials*.
Lets make a plot of the fitted function, along with the standard errors of the fit.

```{r fig.width = 7, fig.height= 6}
agelims = range(age)
age.grid = seq(from = agelims[1], to = agelims[2])
preds = predict(fit, newdata = list(age = age.grid), se = T)
se.bands = cbind(preds$fit + 2*preds$se, preds$fit - 2*preds$se)
plot(age,wage, col = "darkgrey")
lines(age.grid, preds$fit, lwd = 2, col = "blue")
matlines(age.grid, se.bands, col = "blue", lty = 2)

```

There are other more direct ways of doing this in R, For example
```{r}
fita = lm(wage ~ age + I(age^2) + I(age^3) + I(age^4), data = Wage)
summary(fita)
```
Here `I()` is a *wrapper* function; we need it because `age^2` means something to the fomula language, while `I(age^2)` is protected. The coefficients are different to those we got before! However, the fits are the same:
```{r}
plot(fitted(fit), fitted(fita))
```

By using orthogonal polynomials in this simple way, it turns out that we can separately test for each coefficients. So if at the summary again, we can see that the linear, quadratic and cubic terms are significant, but not the quartic.

```{r}
summary(fit)
```
This only works with linear regression, and if there is a single predictor. In general we would use `anova()` as this next example demonstrates.

```{r}
fita = lm(wage ~ education, data = Wage)
fitb = lm(wage ~education+age, data = Wage)
fitc = lm(wage ~education+poly(age,2), data = Wage)
fitd = lm(wage ~ education + poly(age,3), data = Wage)
anova(fita, fitb, fitc,fitd)
```

### Polynomial logistic regression

Now we fit a logistic regression model to a binary response variable,
constructed from `wage`. we code the big earners (`>250K`) as 1 , else 0.
```{r}
fit = glm(I(wage > 250) ~ poly(age,3), data = Wage, family = binomial)
summary(fit)
preds = predict(fit, list(age = age.grid), se = T)
se.bands = preds$fit + cbind(fit = 0, lower = -2*preds$se, upper = 2 *preds$se)
se.bands[1:5,]
```

We have done the complutations on the logit scale. To transform we need to apply the inverse logit mapping.
$$p = \frac{e^\eta}{1+e^\eta}$$
(Here we have used the ability of MarkDown to interpret TeX expression.)
We can do this simultaneously for all three colunms of `se.band`
```{r}
prob.bonds = exp(se.bands)/(1+exp(se.bands))
matplot(age.grid, prob.bonds, col = "blue", lwd=c(2,1,1), lty=c(1,2,2), type = "l", ylim=c(0,1))
points(jitter(age), I(wage>250)/10, pch="|", cex = .5)
